Collocated Deduplication with Fault Isolation for Virtual Machine Snapshot Backup

### 2013-06-21 snapshot_system/append.tex
add snapshot system introduction
add architecture
mwording changes

\section{Append Store}
\subsection{Introduction}
Append Store (AS) is our underlining storage engine for storing snapshot data after deduplication. 
AS is built on top of our highly scalable distributed file system (DFS), 
which is very similar to Google's file system
in a sense that it is optimized for large files and sequential read/append operations.

\subsection{Design considerations}
While scalability has been handled by the DFS, there are still several challenges in 
storing billions of var-sized small data chunks:
\begin{description}
\item[Locality perseveration] Chunk data must be placed next to each other in the order of their writing sequence,
because reading a snapshot incurs large sequential reads of chunks under their logical sequence in the snapshot.
\item[Flexible referencing] To avoid overwhelming metadata operation capbility of DFS's master, 
we have to group small chunks into large data files in DFS.
However, snapshot deletion brings chunk data deletion, and reclaiming disk space would require many chunk data being moved.
If such chunk movement incurs updates of data referencing in snapshot and segment recipes, then the cost of deleting 
a snapshot would be extremely high.
\item[Efficient chunk lookup] The translation from data reference to data location must be very efficient in two ways: 
first, a sorted index is necessary to fast locate the data location in $O(log(n)$ time; 
second, the size of index must be optimized to minimized its memory footprint and the cost of fetching index. 
\end{description}

\subsection{Architecture}
\begin{figure}[htbp]
  \centering
  \epsfig{file=images/append_store_arch.eps, width=3.5in}
  \caption{Architecture of Append Store}
  \label{fig:as_arch}
\end{figure}

>>>>

\section{Append Store}
\label{sect:append}
\subsection{Introduction}
Append Store (AS) is our underlining storage engine for storing snapshot data after deduplication. 
AS is built on top of our highly scalable distributed file system (DFS), 
which is very similar to Google's file system
in a sense that it is optimized for large files and sequential read/append operations.

\subsection{Design considerations}
While scalability has been handled by the DFS, there are still several challenges in 
storing billions of variable-sized small data chunks:
\begin{description}
\item[Locality perseveration] Chunk data must be placed next to each other in the order of their writing sequence,
because reading a snapshot incurs large sequential reads of chunks under their logical sequence in the snapshot.
\item[Flexible referencing] To avoid overwhelming metadata operation capbility of DFS's master, 
we have to group small chunks into large data files in DFS.
However, snapshot deletion brings chunk data deletion, and reclaiming disk space would require many chunks being moved.
If such chunk movement incurs updates of data referencing in snapshot and segment recipes, then the cost of deleting 
a snapshot would be extremely high.
\item[Efficient chunk lookup] The translation from data reference to data location must be very efficient in two ways: 
first, a sorted index is necessary to quickly find the data location in $O(log(n)$ time; 
second, the size of the index must be optimized to minimize its memory footprint and the cost of fetching index. 
\end{description}

\subsection{Architecture}
\begin{figure}[htbp]
  \centering
  \epsfig{file=images/append_store_arch.pdf, width=3.5in}
  \caption{Architecture of Append Store}
  \label{fig:as_arch}
\end{figure}

### 2013-06-21 snapshot_system/failover.tex
mwording changes

@@

%the above model assumes uniform distribution of blocks and doesn't provide compelling numbers
%with 3 replicas, 100 machines, and only 3 failures the chance of a single 10GB VM surviving is 9.11*10^-8
%if we wanted to include it we probably want a model that includes containers, but that might be too complex
%to be useful.
}
\begin{figure}[ht]
  \centering
  %\includegraphics[scale=.45,natwidth=511,natheight=276]{vo_links}
	\begin{tikzpicture}
		\begin{axis}[
		title={VO Block links},
		xlabel={Number of VMs added},
		ylabel={Avg. Block Links},
		%extra y ticks={4.5,5.5,6.5} %because it only shows 4,5,6,7
		legend pos=south east
		]
		\addplot[color=blue,mark=*] table[x=VMs,y=Measured] {figures/vo_links.txt};
		\addplot[color=red,mark=square*] table[x=VMs,y=Theoretical] {figures/vo_links.txt};
		\legend{Measured,Theoretical};
		\end{axis}
	\end{tikzpicture}
  \caption{Average number of VMs sharing a block in the global index}
  \label{fig-vo-links}
\end{figure}
\comments{
	=  sum _for_all_block(   Probablity (a block fails) *number of VM sharing this block ))
               = Probability(a block fails) * sum_for_all_blocks (numb of VM shared)
	= Probablity (a block fails) *b *aveageLengthVM
	= [ 1-  C(r, k) /C(n,r)] * b* [ 1+ s *V(1-1/ln V)]

>>>>

The rate of increase in node failures can be seen in Figure~\ref{fig-vm-failure}
(for a 100 node cluster).
The graph assumes 10X40GB snapshots per VM with 18\% unique data after local
dedup and 64MB filesytem chunks (which results in 1792 filesystem chunks per
VM). We assume 18\% unique data after local dedup because that is what our
snapshots have shown.

\begin{figure}[ht]
  \centering
  %\includegraphics[scale=.45,natwidth=511,natheight=276]{vo_links}
	\begin{tikzpicture}
		\begin{axis}[
		%title={Node failure affect on VMs},
		xlabel={Number of nodes failed},
		ylabel={chance that a VM is affected (\%)},
		%extra y ticks={4.5,5.5,6.5} %because it only shows 4,5,6,7
		]
		\addplot[color=blue,mark=*] table{figures/vm_failure.txt};
		\end{axis}
	\end{tikzpicture}
  \caption{Percent chance that a VM is affected as storage nodes fail}
  \label{fig-vm-failure}
\end{figure}

@@

%the above model assumes uniform distribution of blocks and doesn't provide compelling numbers
%with 3 replicas, 100 machines, and only 3 failures the chance of a single 10GB VM surviving is 9.11*10^-8
%if we wanted to include it we probably want a model that includes containers, but that might be too complex
%to be useful.
}

Figure~\ref{fig-vo-links} shows the average number of links to a given block in the global index as more VMs are added. The first 15 VMs are all windows machines, so that explains the initial higher values, but for the most part the average number of links is between 1.5 and 2.

\begin{figure}[ht]
  \centering
  %\includegraphics[scale=.45,natwidth=511,natheight=276]{vo_links}
	\begin{tikzpicture}
		\begin{axis}[
		%title={VO Block links},
		xlabel={Number of VMs added},
		ylabel={Avg. Links to a Block},
		%extra y ticks={4.5,5.5,6.5} %because it only shows 4,5,6,7
		legend pos=south east
		]
		\addplot[color=blue,mark=*] table[x=VMs,y=Measured] {figures/vo_links.txt};
		\addplot[color=red,mark=square*] table[x=VMs,y=Theoretical] {figures/vo_links.txt};
		\legend{Measured,Theoretical};
		\end{axis}
	\end{tikzpicture}
  \caption{Average number of VMs sharing a block in the global index}
  \label{fig-vo-links}
\end{figure}
\comments{
	=  sum _for_all_block(   Probablity (a block fails) *number of VM sharing this block ))
               = Probability(a block fails) * sum_for_all_blocks (numb of VM shared)
	= Probablity (a block fails) *b *aveageLengthVM
	= [ 1-  C(r, k) /C(n,r)] * b* [ 1+ s *V(1-1/ln V)]
